Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 1114

\begin{proof}
%new added
    Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
    According to Lemma \ref{lem: control of mgtrs}, there exists a constant \added{$C_0>0$}, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
    \begin{align}
        \mathbb{P}_{\mu}\big[\big|e^{\alpha(t-s)}\|X_s\|-e^{\alpha(t-r)}\|X_r\|\big|^{1+\gamma}\big]
        \deleted{=\mathbb{P}_{\mu}[|M_1^t(r,s)|^{1+\gamma}]}
        \leq \added{C_0}e^{\alpha t+(t-s)\deleted{(}\alpha\gamma\deleted{-(1+\gamma)b)}}.
    \end{align}
    Dividing both sides by $e^{\alpha t(1+\gamma)}$, we get
    \begin{align}
        \mathbb{P}_{\mu}\left|W_s-W_r\right|^{1+\gamma}\leq  \added{C_0} e^{-\alpha \gamma s}.
    \end{align}
    Then \added{there is a $C>0$,} for any $0\leq s<t$,
\deleted{
    \begin{align}
       & \|W_t-W_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq \|W_{\lfloor s \rfloor +1}-W_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+2}^{\lfloor t \rfloor}\|W_k-W_{k-1}\|_{\mathbb{P}_{\mu};1+\gamma}+\|W_t-W_{\lfloor t \rfloor}\|_{\mathbb{P}_{\mu};1+\gamma}
       \\&\leq C_{\ref{lem: control of Wt}}e^{-\frac{\alpha \gamma}{1+\gamma}s}\leq C_{\ref{lem: control of Wt}}e^{-\frac{\alpha}{2}s}.
    \end{align}
}
\added{
\begin{align}
	& \|W_t-W_s\|_{\mathbb{P}_{\mu};1+\gamma}
	\leq \|W_{\lfloor s \rfloor+1}-W_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|W_{k+1}-W_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|W_t-W_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{\alpha \gamma s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{\alpha \gamma k}{1+\gamma}}+ e^{-\frac{\alpha \gamma t}{1+\gamma}}\Big)
	\leq Ce^{-\frac{\alpha \gamma}{1+\gamma}s}\leq Ce^{-\frac{\alpha}{2}s}.
\end{align}	
}
\end{proof}
As $\|X_t\|$ is an continuous state branching process with initial mass $\|\mu\|$.
for any $\lambda>0$, $\|X_t\|$ satisfies, see \cite[Chapter 3]{Li2011Measure-valued}, for example.
\begin{align}\label{CSBP}
    \mathbb{P}_{\mu}e^{-\lambda\|X_t\|}=e^{-\|\mu\|v_t(\lambda)}
\end{align}
where $v_t(\lambda)$ is the unique local bounded solution to the equation
\begin{align*}
    \frac{\partial}{\partial t}v_t(\lambda)=-\psi(v_t(\lambda)), \quad  v_0(\lambda)=\lambda,  \quad \lambda>0, t\geq 0.
\end{align*}

In this paper, for any $\beta\in (0,1)$, $v_t(\lambda)$ has explicit expression \cite[Example 3.1]{Li2011Measure-valued}
\begin{align*}
    v_t(\lambda)=\frac{e^{\alpha t} \lambda}{[1+\frac{1}{\alpha}(e^{\alpha \beta t}-1)\lambda^{\beta}]^{1/\beta}}=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0.
\end{align*}
If we fix $t>0$, $v_t(\lambda)$ is increasing corresponding to $\lambda$.

Recall that the superprocess $X$'s extinction probability $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$, where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$. Denote $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$, by equation (3.48) in \cite{Li2011Measure-valued} and formula \eqref{CSBP}, we easily get
\begin{align}
    \mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\alpha^*)}}{1-e^{-\|\mu\|\alpha^*}}\nonumber\\
        &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|. \label{laplaceexpress}
\end{align}

We want to prove the following Lemma
\added{
\begin{lem}\label{lem: control of XT}
	For each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C>0$ such that for each function $f:[0,\infty)\to [1,\infty)$ and each $t\geq 0$ we have
\begin{align}
    \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)\leq C \Big(\frac{f(t)}{e^{\alpha t}}\Big)^{\beta}.
\end{align}
\end{lem}
}
\begin{proof}
 \deleted{Without loss of generality, we assume that $\|\mu\|=1$,} By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
\added{
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]\\
    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|.
\end{align*}
}
	Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t}$ where $t\geq 0,\lambda\geq0$ then $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
\added{Note that}
\begin{align*}
    \left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|&\leq\frac {\alpha^{1/\beta}}{\beta} \left|w_t(\lambda)-w_t(\lambda+\alpha^*)\right| \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\\
    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\alpha^*)^{\beta}}\right|e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\\
    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}.
\end{align*}
Therefore, \added{for each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C_0>0$ such that for each non-negative function $f$ on $[0,\infty),$ each $\lambda \geq 0$ and each $t\geq 0$ we have }
\begin{align}
\label{eq: inequality before take lambda}
    \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)
    \leq C_0e^{\lambda f(t)}\frac{1}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}.
\end{align}
\deleted{
Take $\lambda=\frac{1}{f(t)}$ into the above inequality, we have
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\cdot\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}\exp(\beta(\ln f(t)-\alpha t))
\end{align*}
}
Notice that
\begin{align*}
    w_t(s)^{-1/\beta-1}&\leq \frac{1}{(\alpha s^{-\beta}e^{-\alpha \beta t})^{1/
    \beta+1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta t})^{1/\beta+1}}\mathbf{1}_{t\geq 1}\\
    &\added{\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.}
\end{align*}
This is to say \added{for each $\lambda \in [0,1]$,
\begin{align*}
    \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}
    &\leq\sup_{s\in [\lambda,\lambda+\alpha^*]}\frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
    &\leq \frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}} =: C_1.
\end{align*}
}
\added{Finally, taking $\lambda = f(t)^{-1} \in [0,1]$ back to \eqref{eq: inequality before take lambda} and using the above inequality, we get the desired result.}
\end{proof}
	Define $\mathcal{A}_t(\epsilon):=\{ \|X_t\|\in \|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\}$ where $\epsilon,t>0$.
\deleted{
\begin{lem}\label{lem: control of AT}
  For any $\epsilon,t>0$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exists $C>0$ and $\delta>0$ such that
  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C e^{-\delta t}.$$
\end{lem}
}
\added{
\begin{lem}\label{lem: control of AT}
  For each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$ there exists $C>0$ such that for each $t\geq 0$ we have
  $
  \mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C e^{-\beta\epsilon t}.
  $
\end{lem}
}

\begin{proof}
    First, for any $\epsilon>0$, using Markov inequality, \added{we get for each $\epsilon>0$ and $t\geq 0$,}
\added{
\begin{align}
    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})
    \leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}
	= \frac{\mathbb P_\mu[\|X_t\|\mathbf 1_{D^c}]}{\mathbb P_\mu(D^c)\|\mu\|e^{(\alpha+\epsilon)t}}
    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}e^{-\epsilon t}.
\end{align}
}
    For another side, using Lemma \ref{lem: control of XT}, we have
    $$\mathbb{\tilde{P}}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq C_0 e^{-\beta\epsilon t}, $$
    \added{for some constant $C_0>0$ not related to $\epsilon>0$ and $t\geq 0$.}
\deleted{To finish the proof we write $C_{\ref{lem: control of AT}}=C_{\ref{lem: control of XT}}+1/\mathbb{P}_{\mu}(D^c)$ and $\delta_{\ref{lem: control of AT}}=\beta\epsilon $.}
\begin{comment}
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq \mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})+\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq(C_4+\frac{1}{\mathbb{P}_{\mu}(D^c)})e^{-\beta \epsilon t }
\end{align*}
\end{comment}
\end{proof}

%\subsection{Parameter $m_k[g]$}
\subsection{Parameters}
\added{
 Recall the definition of operator $Z_1$ in \eqref{eq: def of Zf} and the invariant density $\varphi$ in \eqref{invariantdensity}, define
 \begin{align}\label{parameter_mk}
      m_t[f]:=e^{-\alpha (t+1)}\int_{\mathbb R^d} (Z_1T_t^{\alpha}f)(x)\varphi(x)dx,\quad t\geq 0, f\in \mathcal P.
 \end{align}
 }
 \added{
 Using the same argument as in the proof of \cite[Lemma2.7, Lemma4.2 \& Lemma 5.1]{MM}, we can show that
 \begin{lem}\label{lem: control of mk}
For each $f\in\mathcal{P}$, there is a constant $C>0$ such that for each $t\geq 0$, we have
$$|m_t[f]|\leq C_{\ref{lem: control of mk}} e^{(\alpha\beta-\kappa_fb(1+\beta))t}.$$
Therefore, $m_t[f]$ is well-defined.
\end{lem}
Let
\begin{align}
    \phi(x)=\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p(x),~x\in \mathbb{R}^d, p \in\mathbb{N}_0^d.
\end{align}
i.e. $\phi$ is the projection of $f$ onto the $\kappa_f$-eigenspace.
\begin{lem}\label{lemma210}
Let $f \in \mathcal{P}$, $\kappa_f\geq 1$ and $\alpha\beta=\kappa(f)b(1+\beta)$, then the following limit exists:
\begin{align}
    \tilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\added{\lfloor t \rfloor}}m_k[f]=\langle\Psi_0(-i\phi),\varphi\rangle.
\end{align}
\end{lem}

\begin{lem}\label{lemma211}
Let $f\in \mathcal{P}$, assume $\alpha\beta<\kappa_fb(1+\beta)$, if $\kappa_f\geq 1$, the series $\sum_{k=0}^{\infty}m_k[f]$ is absolutely convergent, hence we can define
\begin{align}
    m[f]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx \label{msmallcase}
\end{align}
\end{lem}
 }
\deleted{
\begin{proof}[proof of Lemma 2.14]

	Let $(R,S)$ be the $(1+\beta)$-control-pair corresponding to \ref{lem: upper bound for usgx}(7).
	For each $t\geq 0$,
\begin{align}
    |Z_1(T^{\alpha}_t f)|
    \leq R|T^{\alpha}_tf|
    \leq R (e^{(\alpha-\kappa_fb)t}Qf)
    \leq S(e^{(\alpha-\kappa_fb)t}Qf)
    =e^{(\alpha-\kappa_fb)(1+\beta)t}SQf.
    \end{align}
Therefore,
\[
	|m_t[f]|\leq e^{-\alpha}e^{-\alpha t}e^{(\alpha-\kappa_fb)(1+\beta)t}\int_{\mathbb R^d}SQf(x)\varphi(x)dx.
	\qedhere
\]

@@

$m_k[f],~f\in \mathcal{P}$ can be expressed in a new way which is convenient for us to consider the limit behavior of itself. Note that,
\begin{align}
    m_k[f]=e^{-\alpha(k+1)}\int_{\mathbb{R}^d}\int_0^1 T_{1-s}^{\alpha}\Psi_0(-iT_{s+k}^{\alpha}f)(x)~ds~\varphi(x)~dx,~~k\in\mathbb{N}.
\end{align}

Using Fubini's Theorem and the fact $\varphi(x)$ is an invariant measure of $(T)_{t\geq 0}$, we get
\begin{align}
    m_k[f]=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}f)(x)~ds~\varphi(x)~dx,~~k\in \mathbb{N}.\label{mkeq}
\end{align}

Let
\begin{align}
    \phi(x)=\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p(x),~x\in \mathbb{R}^d, p \in\mathbb{N}_0^d.
\end{align}
i.e. $\phi$ is the projection of $f$ onto the $\kappa_f$-eigenspace. Easily we get $\kappa_f=\kappa_{\phi}$ and $\kappa_{f-\phi}\geq \kappa_f+1$.

\begin{proof}[Proof of Lemma 2.15]

    Notice that
        \begin{align}\label{parameter of mkphi}
        m_k[\phi]&=\int_{\mathbb{R}^d}\int_k^{k+1} e^{-\alpha s}\Psi_0(-iT_{s}^{\alpha}\phi)(x)~ds~\varphi(x)~dx\\
        &=\int_{\mathbb{R}^d}\Psi_0(-i\phi(x))\varphi (x)~dx=\langle \Psi_0(-i\phi),\varphi\rangle.
    \end{align}

    According to Lemma \ref{lem: Lip of power function}, for any $s\geq 0$,
    \begin{align}
        &\Big|\Psi_0(-iT^{\alpha}_s f)-\Psi_0(-iT^{\alpha}_s\phi)\Big|\leq C_{\ref{lem: Lip of power function}}(|T^{\alpha}_sf|^{\beta}+|T^{\alpha}_s\phi|^{\beta})|T^{\alpha}_s(f-\phi)|
        \\& \leq C_{\ref{lem: Lip of power function}}e^{(\alpha-\kappa_f b)(1+\beta)s}e^{-bs}\big((Qf)^{\beta}+(Q\phi)^{\beta}\big)Q(f-\phi).
    \end{align}
    Therefore, by the condition $\alpha\beta=\kappa_fb(1+\beta)$,
    \begin{align}
        |m_k[f]-m_k[\phi]|&\leq\int_{\mathbb{R}^d}\int_k^{k+1}e^{-\alpha s}\Big|\Psi_0(-iT^{\alpha}_s f)-\Psi_0(-iT^{\alpha}_s\phi)\Big|(x)~ds~\varphi(x)~ds.
        \\&\leq C_{\ref{lem: Lip of power function}}\int_{\mathbb{R}^d}\int_{k}^{k+1} e^{-bs}\big((Qf)^{\beta}+(Q\phi)^{\beta}\big)Q(f-\phi)~ds~ \varphi(x)~dx.
        \\&\leq C_{\ref{lem: Lip of power function}}\langle((Qf)^{\beta}+(Q\phi)^{\beta})Q(f-\phi), \varphi\rangle e^{-bk},\quad k \in \mathbb{N}.
    \end{align}
    Therefore, the limits of $(1/t)\sum_{k=0}^tm_k[f]$ is the same with that of $(1/t)\sum_{k=0}^tm_k[\phi]$.

>>>>

\begin{proof}
%new added
    Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
    According to Lemma \ref{lem: control of mgtrs}, there exists a constant \added{$C_0>0$}, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
    \begin{align}
        \mathbb{P}_{\mu}\big[\big|e^{\alpha(t-s)}\|X_s\|-e^{\alpha(t-r)}\|X_r\|\big|^{1+\gamma}\big]
        \deleted{=\mathbb{P}_{\mu}[|M_1^t(r,s)|^{1+\gamma}]}
        \leq \added{C_0}e^{\alpha t+(t-s)\deleted{(}\alpha\gamma\deleted{-(1+\gamma)b)}}.
    \end{align}
    Dividing both sides by $e^{\alpha t(1+\gamma)}$, we get
    \begin{align}
        \mathbb{P}_{\mu}\left|W_s-W_r\right|^{1+\gamma}\leq  \added{C_0} e^{-\alpha \gamma s}.
    \end{align}
    Then \added{there is a $C>0$,} for any $0\leq s<t$,
\deleted{
    \begin{align}
       & \|W_t-W_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq \|W_{\lfloor s \rfloor +1}-W_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+2}^{\lfloor t \rfloor}\|W_k-W_{k-1}\|_{\mathbb{P}_{\mu};1+\gamma}+\|W_t-W_{\lfloor t \rfloor}\|_{\mathbb{P}_{\mu};1+\gamma}
       \\&\leq C_{\ref{lem: control of Wt}}e^{-\frac{\alpha \gamma}{1+\gamma}s}\leq C_{\ref{lem: control of Wt}}e^{-\frac{\alpha}{2}s}.
    \end{align}
}
\added{
\begin{align}
	& \|W_t-W_s\|_{\mathbb{P}_{\mu};1+\gamma}
	\leq \|W_{\lfloor s \rfloor+1}-W_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|W_{k+1}-W_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|W_t-W_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{\alpha \gamma s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{\alpha \gamma k}{1+\gamma}}+ e^{-\frac{\alpha \gamma t}{1+\gamma}}\Big)
	\leq Ce^{-\frac{\alpha \gamma}{1+\gamma}s}\leq Ce^{-\frac{\alpha}{2}s}.
\end{align}	
}
\end{proof}

\deleted{
As $\|X_t\|$ is an continuous state branching process with initial mass $\|\mu\|$.
for any $\lambda>0$, $\|X_t\|$ satisfies, see \cite[Chapter 3]{Li2011Measure-valued}, for example.
\begin{align}\label{CSBP}
    \mathbb{P}_{\mu}e^{-\lambda\|X_t\|}=e^{-\|\mu\|v_t(\lambda)}
\end{align}
where $v_t(\lambda)$ is the unique local bounded solution to the equation
\begin{align*}
    \frac{\partial}{\partial t}v_t(\lambda)=-\psi(v_t(\lambda)), \quad  v_0(\lambda)=\lambda,  \quad \lambda>0, t\geq 0.
\end{align*}

In this paper, for any $\beta\in (0,1)$, $v_t(\lambda)$ has explicit expression \cite[Example 3.1]{Li2011Measure-valued}
\begin{align*}
    v_t(\lambda)=\frac{e^{\alpha t} \lambda}{[1+\frac{1}{\alpha}(e^{\alpha \beta t}-1)\lambda^{\beta}]^{1/\beta}}=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0.
\end{align*}
If we fix $t>0$, $v_t(\lambda)$ is increasing corresponding to $\lambda$.
}
\added{
    According to \cite[Example 3.1]{Li2011Measure-valued}, we have
\begin{align}\label{CSBP}
    \mathbb{P}_{\mu} [e^{-\lambda\|X_t\|}]
    =e^{-\|\mu\|v_t(\lambda)},
    \quad \lambda \geq 0, t\geq 0,
\end{align}
    where
\[
    v_t(\lambda)=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0.
\]
}

    Recall that the \deleted{superprocess $X$'s} extinction probability \added{of the superprocess is} $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$ where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$. 
    Denote \added{by} $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$. 
    \added{According to \eqref{CSBP} and the markovian property we have for each $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and 
    $t\geq 0$,}
    \label{laplaceexpress}
    \mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]
    &=\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }\mathbb P_\mu(D^c| \mathscr F_t)] }{\mathbb P_\mu(D^c)}
    =\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }(1-e^{-\alpha^*\|X_t\|})] }{\mathbb P_\mu(D^c)}
    \\&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\alpha^*)}}{1-e^{-\|\mu\|\alpha^*}}
    \leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|. 
    \deleted{We want to prove the following Lemma}
\begin{lem}\label{lem: control of XT}
	For each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C>0$ such that for each function $f:[0,\infty)\to [1,\infty)$ and each $t\geq 0$ we have
    \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)\leq C \Big(\frac{f(t)}{e^{\alpha t}}\Big)^{\beta}.
\end{lem}
\begin{proof}
 \deleted{Without loss of generality, we assume that $\|\mu\|=1$,} By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]\\
    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|.
\end{align*}
	Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t}$ where $t\geq 0,\lambda\geq0$ then $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
\added{Note that}
\begin{align*}
    \left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|&\leq\frac {\alpha^{1/\beta}}{\beta} \left|w_t(\lambda)-w_t(\lambda+\alpha^*)\right| \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\\
    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\alpha^*)^{\beta}}\right|e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\\
    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}.
\end{align*}
Therefore, \added{for each $\mu\in \mathcal M_c(\mathbb R^d)$, there is a constant $C_0>0$ such that for each non-negative function $f$ on $[0,\infty),$ each $\lambda \geq 0$ and each $t\geq 0$ we have }
\label{eq: inequality before take lambda}
    \mathbb{\tilde{P}}_{\mu}\big(\|X_t\|\leq f(t)\big)
    \leq C_0e^{\lambda f(t)}\frac{1}{\lambda^{\beta}}e^{-\alpha\beta t} \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}.
Take $\lambda=\frac{1}{f(t)}$ into the above inequality, we have
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\cdot\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}\exp(\beta(\ln f(t)-\alpha t))
\end{align*}
Notice that
\begin{align*}
    w_t(s)^{-1/\beta-1}&\leq \frac{1}{(\alpha s^{-\beta}e^{-\alpha \beta t})^{1/
    \beta+1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta t})^{1/\beta+1}}\mathbf{1}_{t\geq 1}\\
    &\added{\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.}
\end{align*}
\added{Therefore, for each $\lambda \in [0,1]$,
\begin{align*}
    \sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}
    &\leq\sup_{s\in [\lambda,\lambda+\alpha^*]}\frac{s^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta +1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
    &\leq \frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}} =: C_1.
\end{align*}
\added{Finally, taking $\lambda = f(t)^{-1} \in [0,1]$ back to \eqref{eq: inequality before take lambda} and using the above inequality, we get the desired result.}

@@

	Define $\mathcal{A}_t(\epsilon):=\{ \|X_t\|\in \|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\}$ where $\epsilon,t>0$.
\begin{lem}\label{lem: control of AT}
  For any $\epsilon,t>0$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exists $C>0$ and $\delta>0$ such that
  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C e^{-\delta t}.$$
\end{lem}
\begin{lem}\label{lem: control of AT}
  For each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$ there exists $C>0$ such that for each $t\geq 0$ we have
  $
  \mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C e^{-\beta\epsilon t}.
  $
\end{lem}

\begin{proof}
    First, for any $\epsilon>0$, using Markov inequality, \added{we get for each $\epsilon>0$ and $t\geq 0$,}
\added{
\begin{align}
    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})
    \leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}
	= \frac{\mathbb P_\mu[\|X_t\|\mathbf 1_{D^c}]}{\mathbb P_\mu(D^c)\|\mu\|e^{(\alpha+\epsilon)t}}
    \leq \frac{1}{\mathbb{P}_{\mu}(D^c)}e^{-\epsilon t}.
\end{align}
}
    For another side, using Lemma \ref{lem: control of XT}, we have
    $$\mathbb{\tilde{P}}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq C_0 e^{-\beta\epsilon t}, $$
    \added{for some constant $C_0>0$ not related to $\epsilon>0$ and $t\geq 0$.}
\deleted{To finish the proof we write $C_{\ref{lem: control of AT}}=C_{\ref{lem: control of XT}}+1/\mathbb{P}_{\mu}(D^c)$ and $\delta_{\ref{lem: control of AT}}=\beta\epsilon $.}
\end{proof}

\subsection{Parameters}
 Recall the definition of operator $Z_1$ in \eqref{eq: def of Zf} and the invariant density $\varphi$ in \eqref{invariantdensity}, define
 \begin{align}\label{parameter_mk}
      m_t[f]:=e^{-\alpha (t+1)}\int_{\mathbb R^d} (Z_1T_t^{\alpha}f)(x)\varphi(x)dx,\quad t\geq 0, f\in \mathcal P.
 \end{align}
 \deleted{Using the same argument as in the proof of \cite[Lemma2.7, Lemma4.2 \& Lemma 5.1]{MM}, we can show that}
\added{According to \cite[Lemma 2.7]{MM}, for each $f\in\mathcal{P}$, there is a constant $C>0$ such that 
\[
    |m_t[f]|
    \leq C e^{(\alpha\beta-\kappa_fb(1+\beta))t},
    \quad t\geq 0.
\]
}
\deleted{Therefore, $m_t[f]$ is well-defined.}
